---
title: "Statistics Analysis Homework 1"
author: "2015-26042 Hyunghun Cho"
date: "Friday, September 09, 2016"
output: html_document
---

This is an exercise from OpenIntro Statistics <https://www.openintro.org/stat/>.

Firstly, I solved the exercises from **Introduction to data**: <http://htmlpreview.github.io/?https://github.com/andrewpbray/oiLabs-base-R/blob/master/intro_to_data/intro_to_data.html> 

```{r}
source("http://www.openintro.org/stat/data/cdc.R")
names(cdc)
head(cdc)
tail(cdc)
```

**Exercise 1 Answer**
There is 20000 cases for each nine variables like follows: genhlth exerany hlthplan smoke100 height weight wtdesire age gender
Each variables has following data types: categorical discrete discrete discrete discrete discrete discrete discrete categorical

```{r}
str(cdc)
```
**Exercise 2 Answer**

```{r, echo=FALSE}
height <- cdc$height
age <- cdc$age
summary(height)
summary(age)
print (IQR(height))
print (IQR(age))

gender.freq <- table(cdc$gender)
gender.relfreq <- gender.freq / length(cdc$gender)
barplot(gender.relfreq)


print (gender.freq['m'])

exerany.freq <- table(cdc$exerany)
exerany.relfreq <- exerany.freq / length(cdc$exerany)
barplot(exerany.relfreq)

```
**Exercise 3 Answer**
The below plot reveals that male has more smoking habits than female. 
```{r, echo=FALSE}
print (table(cdc$gender,cdc$smoke100))
mosaicplot(table(cdc$gender,cdc$smoke100))

```
**Exercise 4 Answer**

```{r}
under23_and_smoke <- subset(cdc, cdc$smoke100 == 1 & cdc$age > 23)
summary(under23_and_smoke)

```

**Exercise 5 Answer**
Below boxplot shows a trend which the who is well has less BMI Index.  
But, the smokers and non smokers have no significant differences to BMI Index. I thought that smokers may have bad health conditions, but this is a wrong assumption.

```{r, echo=FALSE}
bmi <- (cdc$weight / cdc$height^2) * 703
boxplot(bmi ~ cdc$genhlth)
boxplot(bmi ~ cdc$smoke100)
boxplot(bmi ~ cdc$exerany)

```
It's time to solve the questions in On Your Own.

**On Your Own 1 Answer**
Below figure shows that there is a positive relationship between weight and desired weight.  

```{r, echo=FALSE}
plot(cdc$weight ~ cdc$wtdesire)

```
**On Your Own 2 Answer**

```{r}
wdiff <- cdc$weight - cdc$wtdesire

```

**On Your Own 3 Answer**
wdiff is 0 if a person's desired weight is same as his(her) current weight.
If it is positive, it means that he(she) want to lose his(her) weight. Otherwise he(she) want to put weight on.

```{r}
print (typeof(wdiff))

```
**On Your Own 4 Answer**
Almost people want to lose their weight a little bit. Also, there are outliers who want to lose or to put on many weights.
```{r, echo=FALSE}
print (summary(wdiff))
barplot(wdiff)
boxplot(wdiff)
hist(wdiff, breaks = 50)
```

**On Your Own 5 Answer**
Men and women has no significant differences to view about their weight.

```{r, echo=FALSE}
men <- subset(cdc, cdc$gender == "m")
women <- subset(cdc, cdc$gender == "f")
print (summary(men))
print (summary(women))
men.wdiff <- men$weight - men$wtdesire
women.wdiff <- women$weight - women$wtdesire
boxplot(men.wdiff, women.wdiff, names=c("men wdiff", "women wdiff"))
```

**On Your Own 5 Answer**

```{r}
weight.mean <- mean(cdc$weight)
weight.sd <- sd(cdc$weight)
print (paste(c(weight.mean, weight.sd), collapse=', '))

normalized <- (cdc$weight - weight.mean)/weight.sd
hist(normalized, freq = FALSE)

```